Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model

### 2014-04-12 trunk/paper_enahpc14/Sec4:Evaluation.tex
updates Introduction; refreshes bibliography

\subsection{Measurement methodology}
\label{subsec:4.1}
To analyse the energy  footprint and overall performance of COSMO-ART,
two  important metrics  were  examined: \textit{time-to-solution}  and
\textit{energy-to-solution}.   Time-to-Solution  refers  to the  total
wall clock time of  the application execution time. Energy-to-solution
is the amount  of energy spent to achieve  results. Energy consumption
of CSCS clusters is assessed  by sampling the instantaneous peak power
during  execution  which  is  then  averaged  and  multiplied  by  the
time-to-solution  to determine energy-to-solution.  Whenever possible,
multiple production runs of COSMO-ART were performed to illustrate the
reproducibility  of   the  baseline,  and   quantify  the  significant
uncertainties in  the power measurement, as dictated  by the available
technology.

>>>>

\subsection{Measurement methodology}
\label{subsec:4.1}
We  approach  the  assessment  of  the energy  footprint  and  overall
performance    of    COSMO-ART    with    two    important    metrics:
\textit{time-to-solution}       and       \textit{energy-to-solution}.
Time-to-Solution  refers   to  the  total  wall  clock   time  of  the
application execution time. Energy-to-solution is the amount of energy
spent  to achieve  results.  Energy  consumption of  CSCS  clusters is
assessed  by sampling  the instantaneous  peak power  during execution
which  is then  averaged  and multiplied  by  the time-to-solution  to
determine energy-to-solution.   Whenever possible, multiple production
runs of COSMO-ART were  performed to illustrate the reproducibility of
the baseline, and quantify  the significant uncertainties in the power
measurement, as dictated by the available technology.
